Examples of functions

### 2025-01-14 README.Rmd
adding package summary

The goal of `criticalESvalue` is to ...
<!-- TODO aggiungi qualche riga qui -->

>>>>

The `criticalESvalue` package provide a set of functions to calculate the critical effects size value for the common statistical model. Currently, the package support the `htest` class (i.e., `t.test` and `cor.test`), the `lm` class and the `rma` class from the `metafor` package.

The package contains a set of functions to work with summary data and the `critical()` method that takes objects of class `htest`, `lm` or `rma` and provide enhanced printing and summary methods with information about critical effects size.
